---
title: "Traffic Accident Analysis"
output: html_document
---

## Load packages

```{r}
library(sf)
library(tmap)
library(tmaptools)
library(tidyverse)
library(car)
library(janitor)
library(tidymodels)
library(spatialreg)
library(spgwr)
library(spdep)
library(RColorBrewer)
library(here)
```


## 1. Load map

### Load parliamentary constituencies map uk
#### Shapefile on github url:https://github.com/RuoxuanHong/GISAssessment/tree/main/Parliamentary_Constituencies
```{r}
parliamentaryconstituencies <- st_read(here::here("Westminster_Parliamentary_Constituencies", 
                                 "Westminster_Parliamentary_Constituencies__December_2015__Boundaries.shp"))%>%
  st_transform(., 27700)
qtm(parliamentaryconstituencies)  
```


### load parliamentary constituencies map london
```{r}
londonparliamentaryconstituenciesmap <- parliamentaryconstituencies %>%
  dplyr::filter(str_detect(pcon15cd, "E14000540")|
                str_detect(pcon15cd, "E14000549")|
                str_detect(pcon15cd, "E14000551")|
                  str_detect(pcon15cd, "E14000553")|
                  str_detect(pcon15cd, "E14000555")|
                  str_detect(pcon15cd, "E14000558")|
                  str_detect(pcon15cd, "E14000591")|
                  str_detect(pcon15cd, "E14000592")|
                  str_detect(pcon15cd, "E14000593")|
                  str_detect(pcon15cd, "E14000604")|
                  str_detect(pcon15cd, "E14000615")|
                  str_detect(pcon15cd, "E14000621")|
                  str_detect(pcon15cd, "E14000629")|
                  str_detect(pcon15cd, "E14000634")|
                  str_detect(pcon15cd, "E14000636")|
                  str_detect(pcon15cd, "E14000639")|
                  str_detect(pcon15cd, "E14000654")|
                  str_detect(pcon15cd, "E14000655")|
                  str_detect(pcon15cd, "E14000656")|
                  str_detect(pcon15cd, "E14000657")|
                  str_detect(pcon15cd, "E14000673")|
                  str_detect(pcon15cd, "E14000674")|
                  str_detect(pcon15cd, "E14000675")|
                  str_detect(pcon15cd, "E14000676")|
                  str_detect(pcon15cd, "E14000679")|
                  str_detect(pcon15cd, "E14000687")|
                  str_detect(pcon15cd, "E14000690")|
                  str_detect(pcon15cd, "E14000691")|
                  str_detect(pcon15cd, "E14000692")|
                  str_detect(pcon15cd, "E14000696")|
                  str_detect(pcon15cd, "E14000701")|
                  str_detect(pcon15cd, "E14000703")|
                  str_detect(pcon15cd, "E14000718")|
                  str_detect(pcon15cd, "E14000720")|
                  str_detect(pcon15cd, "E14000721")|
                  str_detect(pcon15cd, "E14000726")|
                  str_detect(pcon15cd, "E14000727")|
                  str_detect(pcon15cd, "E14000731")|
                  str_detect(pcon15cd, "E14000732")|
                  str_detect(pcon15cd, "E14000737")|
                  str_detect(pcon15cd, "E14000741")|
                  str_detect(pcon15cd, "E14000750")|
                  str_detect(pcon15cd, "E14000751")|
                  str_detect(pcon15cd, "E14000752")|
                  str_detect(pcon15cd, "E14000759")|
                  str_detect(pcon15cd, "E14000760")|
                  str_detect(pcon15cd, "E14000763")|
                  str_detect(pcon15cd, "E14000764")|
                  str_detect(pcon15cd, "E14000768")|
                  str_detect(pcon15cd, "E14000770")|
                  str_detect(pcon15cd, "E14000787")|
                  str_detect(pcon15cd, "E14000788")|
                  str_detect(pcon15cd, "E14000789")|
                  str_detect(pcon15cd, "E14000790")|
                  str_detect(pcon15cd, "E14000823")|
                  str_detect(pcon15cd, "E14000869")|
                  str_detect(pcon15cd, "E14000872")|
                  str_detect(pcon15cd, "E14000882")|
                  str_detect(pcon15cd, "E14000887")|
                  str_detect(pcon15cd, "E14000896")|
                  str_detect(pcon15cd, "E14000900")|
                  str_detect(pcon15cd, "E14000906")|
                  str_detect(pcon15cd, "E14000978")|
                  str_detect(pcon15cd, "E14000984")|
                  str_detect(pcon15cd, "E14000998")|
                  str_detect(pcon15cd, "E14001002")|
                  str_detect(pcon15cd, "E14001005")|
                  str_detect(pcon15cd, "E14001007")|
                  str_detect(pcon15cd, "E14001008")|
                  str_detect(pcon15cd, "E14001013")|
                  str_detect(pcon15cd, "E14001032")|
                  str_detect(pcon15cd, "E14001036")|
                  str_detect(pcon15cd, "E14001040"))%>%
  st_transform(., 27700)

  qtm(londonparliamentaryconstituenciesmap)
```
  
  
  
## 2. Load traffic accident dataset

#### csv file on Github url:https://github.com/RuoxuanHong/GISAssessment/raw/main/traffic_accident_data.csv
```{r}
  Trafficaccidentprofile <- read_csv("traffic_accident_data.csv", 
                                 col_names = TRUE, 
                                 locale = locale(encoding = 'Latin1'))
```

### Map traffic accident
```{r}
Trafficaccidentnumber <- londonparliamentaryconstituenciesmap%>%
    left_join(.,
              Trafficaccidentprofile, 
              by = c("pcon15cd" = "Ons code"))
  

tmap_mode("view")
  qtm(Trafficaccidentnumber, 
      fill = "all_accidents", 
      borders = NULL,  
      fill.palette = "Blues")
```
  
  
  
## 3. Traffic accidents data transformation

### Distribution of traddic accidents
```{r}
Trafficaccidentnumber <- Trafficaccidentnumber %>%
    clean_names()

ggplot(Trafficaccidentnumber, aes(x=all_accidents)) + 
    geom_histogram(aes(y = ..density..),
                   binwidth = 100) + 
    geom_density(colour="red", 
                 size=1, 
                 adjust=1)
```

### Tukey
```{r}
symbox(~all_accidents, 
       Trafficaccidentnumber, 
       na.rm=T,
       powers=seq(-3,3,by=.25)) 
```

### Plot transformed dependent variable distribution
```{r}
ggplot(Trafficaccidentnumber, aes((x=all_accidents)^-0.75) )+ 
  geom_histogram(aes(y = ..density..),
                 binwidth = 0.003) + 
  geom_density(colour="red", 
               size=1, 
               adjust=1)
```



## 4. Spatial Weight matrix

###Calculate the centroids of all parliamentary constituencies
```{r}
coordsW <- Trafficaccidentnumber%>%
  st_centroid()%>%
  st_geometry()

plot(coordsW)
```

### Queen's case and nerest neighbours comparison
```{r}
LWard_nb <- Trafficaccidentnumber %>%
  poly2nb(., queen=T)


knn_wards <-coordsW %>%
  knearneigh(., k=4)

LWard_knn <- knn_wards %>%
  knn2nb()

plot(LWard_nb, st_geometry(coordsW), col="red")

plot(LWard_knn, st_geometry(coordsW), col="blue")
```

### KNN4 spatial weight matrix
```{r}
Lward.knn_4_weight <- LWard_knn %>%
  nb2listw(., style="C")
```


## 5. traffic accident spatial analysis

### Moran's I
```{r}
Trafficaccidentnumbermoran <- Trafficaccidentnumber %>%
  st_drop_geometry()%>%
  dplyr::select(all_accidents)%>%
  pull()%>%
  moran.test(., Lward.knn_4_weight)
Trafficaccidentnumbermoran
```


### Traffic accident Geary's C
```{r}
TrafficaccidentnumberGeary <- Trafficaccidentnumber %>%
  st_drop_geometry()%>%
  dplyr::select(all_accidents)%>%
  pull()%>%
  geary.test(., Lward.knn_4_weight)
TrafficaccidentnumberGeary
```


### Getis Ord General G
```{r}
TrafficaccidentnumberG <- Trafficaccidentnumber %>%
  st_drop_geometry()%>%
  dplyr::select(all_accidents)%>%
  pull()%>%
  globalG.test(., Lward.knn_4_weight)
TrafficaccidentnumberG
```


### local Moran's I
```{r}
Trafficaccidentnumberlocalmoran <- Trafficaccidentnumber %>%
  st_drop_geometry()%>%
  dplyr::select(all_accidents)%>%
  pull()%>%
  localmoran(., Lward.knn_4_weight)%>%
  as_tibble()
Trafficaccidentnumberlocalmoran
```

### Map local Moran's I
```{r}
Trafficaccidentnumber <- Trafficaccidentnumber %>%
  mutate(all_accidents_I = as.numeric(Trafficaccidentnumberlocalmoran$Ii))%>%
  mutate(all_accidents_Iz =as.numeric(Trafficaccidentnumberlocalmoran$Z.Ii))

# set the breaks and colour
breaks1<-c(-1000,-2.58,-1.96,-1.65,1.65,1.96,2.58,1000)
MoranColours<- rev(brewer.pal(8, "RdGy"))

# Local Moran's I map
tm_shape(Trafficaccidentnumber) +
  tm_polygons("all_accidents_Iz",
              style="fixed",
              breaks=breaks1,
              palette=MoranColours,
              midpoint=NA,
              title="Local Moran's I, Traffic Accidents in London")
```

### Local G map
```{r}
TrafficaccidentnumberGi <- Trafficaccidentnumber %>%
  st_drop_geometry()%>%
  dplyr::select(all_accidents)%>%
  pull()%>%
  localG(., Lward.knn_4_weight)
TrafficaccidentnumberGi


Trafficaccidentnumber <- Trafficaccidentnumber %>%
  mutate(all_accidents_G = as.numeric(TrafficaccidentnumberGi))

GIColours<- rev(brewer.pal(8, "RdBu"))

# plot
tm_shape(Trafficaccidentnumber) +
  tm_polygons("all_accidents_G",
              style="fixed",
              breaks=breaks1,
              palette=GIColours,
              midpoint=NA,
              title="Gi*, Traffic Accidents in London")
```



## 6. Multiple Linear regression

### Model 1
```{r}
Regressiondata<- Trafficaccidentnumber%>%
  clean_names()%>%
  dplyr::select(all_accidents, 
                cars_per_household,
                travel_by_bicycle_to_work,
                employment_rate,
                public_transport_accessibility,
                population_density,
                area_of_road)

model1 <- Regressiondata %>%
  lm(all_accidents^-0.75 ~
       cars_per_household+
       travel_by_bicycle_to_work+
       employment_rate+
       public_transport_accessibility+
       population_density+
       area_of_road,
     data=.)
summary(model1)
```



### vif test
```{r}
vif(model1)
```


### Model2
```{r}
model2 <- Regressiondata %>%
  lm(all_accidents^-0.75 ~
       cars_per_household+
       travel_by_bicycle_to_work+
       employment_rate+
       public_transport_accessibility,
     data=.)
summary(model2)
```


### Model3
```{r}
model3 <- Regressiondata %>%
  lm(all_accidents^-0.75 ~
       employment_rate+
       public_transport_accessibility,
     data=.)
summary(model3)
```


### Lagrange Multiplier Diagnostics
```{r}
lm.LMtests(model3,Lward.knn_4_weight, zero.policy=NULL, test="all", spChk=NULL, naSubset=TRUE)
```


### Print some model diagnositcs. 
```{r}
par(mfrow=c(2,2))
plot(model3)
```


### Durbin-Watson test
```{r}
DW <- durbinWatsonTest(model3)
tidy(DW)
```


### Write the residuals outand add them to the shapelayer
```{r}
model_data3 <- model3 %>%
  augment(., Regressiondata)


Trafficaccidentnumber <- Trafficaccidentnumber %>%
  mutate(model3resids = residuals(model3))
```


## 7. SLM and SEM to include spatial elements

### plot the residuals
```{r}
tmap_mode("view")

tm_shape(Trafficaccidentnumber) +
  tm_polygons("model3resids",
              palette = "RdYlBu")
```


### residual moran's I
```{r}
Nearest_neighbour <- Trafficaccidentnumber %>%
  st_drop_geometry()%>%
  dplyr::select(model3resids)%>%
  pull()%>%
  moran.test(., Lward.knn_4_weight)%>%
  tidy()

Nearest_neighbour
```



### Spatially lagged model
```{r}
slag_dv_model3_knn4 <- lagsarlm(all_accidents^-0.75 ~
                                  employment_rate+
                                  public_transport_accessibility,
                                data=Trafficaccidentnumber, 
                                nb2listw(LWard_knn, 
                                         style="C"), 
                                method = "eigen")

summary(slag_dv_model3_knn4)
```


#### Residual Moran test on SLM
```{r}
Trafficaccidentnumber <- Trafficaccidentnumber %>%
  mutate(slag_dv_model3_knn_resids = residuals(slag_dv_model3_knn4))

KNN4Moran <- Trafficaccidentnumber %>%
  st_drop_geometry()%>%
  dplyr::select(slag_dv_model3_knn_resids)%>%
  pull()%>%
  moran.test(., Lward.knn_4_weight)%>%
  tidy()
KNN4Moran
```


### Spatial error model
```{r}
sem_model1 <- errorsarlm(all_accidents^-0.75 ~
                           employment_rate+
                           public_transport_accessibility,
                         data=Trafficaccidentnumber,
                         nb2listw(LWard_knn, style="C"), 
                         method = "eigen")

tidy(sem_model1)
summary(sem_model1)
```

#### Residual Moran test on SEM
```{r}
Trafficaccidentnumber <- Trafficaccidentnumber %>%
  mutate(sem_model1 = residuals(sem_model1))

KNN4Moranerr <- Trafficaccidentnumber %>%
  st_drop_geometry()%>%
  dplyr::select(sem_model1)%>%
  pull()%>%
  moran.test(., Lward.knn_4_weight)%>%
  tidy()
KNN4Moranerr
```


## 8. GWR

#### Transformation
```{r}
st_crs(Trafficaccidentnumber) = 27700

TrafficaccidentnumberSP <- Trafficaccidentnumber %>%
  as(., "Spatial")

st_crs(coordsW) = 27700

coordsWSP <- coordsW %>%
  as(., "Spatial")
coordsWSP
```

### Calculate kernel bandwidth
```{r}
GWRbandwidth <- gwr.sel(all_accidents^-0.75 ~
                          employment_rate+
                          public_transport_accessibility, 
                        data = TrafficaccidentnumberSP, 
                        coords=coordsWSP,
                        adapt=T)
```

### Run the gwr model
```{r}
gwr.model = gwr(all_accidents^-0.75 ~
                  employment_rate+
                  public_transport_accessibility, 
                data = TrafficaccidentnumberSP, 
                coords=coordsWSP, 
                adapt=GWRbandwidth, 
                hatmatrix=TRUE, 
                se.fit=TRUE)

gwr.model
```


```{r}
results <- as.data.frame(gwr.model$SDF)
names(results)
```


### Attach coefficients to original SF
```{r}
Trafficaccidentnumber2 <- Trafficaccidentnumber %>%
  mutate(coefEmployment = results$employment_rate,
         coefTransport = results$public_transport_accessibility)
```

### Employment rate coefficient plot
```{r}
tm_shape(Trafficaccidentnumber2) +
  tm_polygons(col = "coefEmployment", 
              palette = "-RdBu", 
              alpha = 0.9)
```

### Public transport accessbility coefficient plot
```{r}
tm_shape(Trafficaccidentnumber2) +
  tm_polygons(col = "coefTransport", 
              palette = "RdBu", 
              alpha = 0.9)
```


### Run the significance test
```{r}
sigTest = abs(gwr.model$SDF$"public_transport_accessibility")-2 * gwr.model$SDF$"public_transport_accessibility_se"
sigTest1 = abs(gwr.model$SDF$"employment_rate")-2 * gwr.model$SDF$"employment_rate_se"
```

### Store significance results
```{r}
Trafficaccidentnumber2 <- Trafficaccidentnumber2 %>%
  mutate(GWREmploymentSig = sigTest)

tm_shape(Trafficaccidentnumber2) +
  tm_polygons(col = "GWREmploymentSig", 
              palette = "RdYlBu")
```
